---
title: 'Assignment A01: GGPLOT2'
author: Ramin Ala
date: '2021-05-19'
slug: assignment-a01-ggplot2
categories:
  - ggplot2
tags: []
---

1. Introduction:

  In this post, the solution for assignment 01 is provided. I selected "ChickWeight" dataset because it consists of both Numerical and Categorical data.
  This data frame has 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks. This dataset has two numeric variables:
  
  weight: weight of specific chick at specific day (Time), and
  
  Time: Number of days  since birth to measurement day, 
  
  as well as two ordered variables:
  
  Chick: identifier of chick. from 1 to 48, and
  
  Diet: 4 different applied diets.
  
  Lets take a look at data:

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(datasets)

head(ChickWeight)

```

2. plots

## categorical

```{r  warning=FALSE, echo=FALSE, message=FALSE}

# First we're going to make a background dataset with the diet variable removed. 


ggplot(ChickWeight, aes(Time, weight)) +
  geom_point() 


```



## numerical

```{r}

ggplot(ChickWeight, aes(Time, weight)) +
  geom_point() 


```


3. discussion


kkkkkkkkkkkkkkkkkkkkkk