---
title: 'Assignment A01: GGPLOT2'
author: Ramin Ala
date: '2021-05-19'
slug: assignment-a01-ggplot2
categories:
  - ggplot2
tags: []
---

1. Introduction:

  In this post, the solution for assignment 01 is provided. I selected "ChickWeight" dataset because it consists of both Numerical and Categorical data.
  This data frame has 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks. This dataset has two numeric variables:
  
  weight: weight of specific chick at specific day (Time), and
  
  Time: Number of days  since birth to measurement day, 
  
  as well as two ordered and categorical variables:
  
  Chick: identifier of chick. from 1 to 48, and
  
  Diet: 4 different applied diets.
  
  Lets take a look at data:

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(datasets)

head(ChickWeight)

```

2. plots

## categorical

Plot mean of chick weight at birthday and day 21 in terms of four different diet plans.

```{r  warning=FALSE, echo=FALSE, message=FALSE}

library(dplyr)

ChickWeight_reorganized <-  filter(ChickWeight, (Time == 0) | (Time == 21)) %>%
  group_by(Diet, Time) %>%
  summarise(Mean = mean(weight))

ChickWeight_reorganized$Time <- as.factor(ChickWeight_reorganized$Time) 

ggplot(ChickWeight_reorganized, aes(x=Diet, y=Mean, fill=Time)) +
  geom_bar(stat="identity", position=position_dodge()) +
  labs(title="Mean of chick weight", x= "Diat plans", y= "mean of chick weight")
 
 
```



## numerical

```{r}

# First we're going to make a background dataset with the diet variable removed. 
ChickWeight_bg <- ChickWeight %>% filter((Time == 0) | (Time == 21)) %>% select(-Diet)

# let's group the data by each chick; this will carry out any subsequent geoms for each chick
ggplot(ChickWeight, aes(Time, weight, color = Diet, group = Chick))+
  geom_line() + # line plot
  facet_wrap(~Diet)

```


3. discussion

  From bar chart, it seems the diet 3 results in the heaviest chicks in average on the day 21, followed by diet 4,diet 2, and diet 1.Besides, average weight at birthda prove that chicks have approximately the same weight at day 0.
  
  