---
title: 'Assignment A01: GGPLOT2'
author: Ramin Ala
date: '2021-05-19'
slug: assignment-a01-ggplot2
categories:
  - ggplot2
tags: []
---

1. Introduction:

  In this post, the solution for assignment 01 is provided. I selected "ChickWeight" dataset because it consists of both Numerical and Categorical data.
  This data frame has 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks. This dataset has two numeric variables:
  
  weight: weight of specific chick at specific day (Time), and
  
  Time: Number of days  since birth to measurement day, 
  
  as well as two ordered and categorical variables:
  
  Chick: identifier of chick. from 1 to 48, and
  
  Diet: 4 different applied diets.
  
  Lets take a look at data:

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(datasets)

head(ChickWeight)

```

2. plots

## categorical

aaa

```{r  warning=FALSE, echo=FALSE, message=FALSE}

#library(dplyr)
#Mean = mean(ChickWeight$weight)
#Mean
cw_summary <-  filter(ChickWeight, (Time == 0) | (Time == 21)) %>%
  group_by(Diet, Time) %>%
  summarise(Mean = mean(weight),se = sd(weight)/(sqrt(n())))

cw_summary$Time <- as.factor(cw_summary$Time) 

ggplot(cw_summary, aes(x=Diet, y=Mean, fill=Time)) + # aesthetics
  geom_bar(stat="identity", position=position_dodge()) # geom for bar plots
  
 
 
```



## numerical

```{r}

ggplot(ChickWeight, aes(Time, weight)) +
  geom_point() 



  

```


3. discussion


kkkkkkkkkkkkkkkkkkkkkk