---
title: 'Assignment A03: Tidyverse'
author: ''
date: '2021-06-02'
slug: assignment-a03-tidyverse
categories: []
tags: []
---

Use the attached file lego_sales.csv and complete the following tasks using tidyverse. Submit the RmD file and link to the post on your website.


```{r}

library(tidyverse)

lego <- read_csv("lego_sales.csv")

head(lego)
glimpse(lego)
names(lego)

```


## 1- What are the three most common first names of customers?

```{r}

lego %>%
    select(first_name) %>%
    count(first_name) %>%
    arrange(desc(n))

```
answer: 1-Jackson (13) 2,3- Jacob (11) , Jacob (11) are three most popular first names.

## 2- What are the three most common themes of lego sets purchased?

```{r}
lego %>%
    select(theme) %>%
    count(theme) %>%
    arrange(desc(n))
```

answer: 1-Star Wars (75) 2- Nexo Knights (64) 3- Gear & Mixels (55-tie) are common themes of lego sets purchased.

## 3- Among the most common theme of lego sets purchased, what is the most common subtheme?



    
## 4- Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”. Be sure to save the updated data set so you can use the new variable in other questions.
    

## What is the probability a randomly selected customer
        is in the 19 - 25 age group?
        is in the 19 - 25 age group and purchased a Duplo theme set?
        is in the 19 - 25 age group given they purchased a Duplo theme set?  

## Which age group has purchased the largest number of lego sets? How many did they purchase? 

    
## Which age group has spent the most money on legos? How much did they spend?
    


## Come up with a question you want to answer using this data, and write it down. Then, create a data visualization that answers the question, and briefly explain how your visualization answers the question.
    
## Add one element to the plot from the previous exercise to change the look of the plot without changing the underlying data. For example, you can change the theme, background color, add annotations, etc. State the change you’re making and display the updated visualization. We encourage you to be creative!
    
